---
title: "Introduction to numhelpr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to numhelpr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(numhelpr)
```
## Why numhelpr?
Working with numbers in R often requires writing the same small formulas over and over again. `numhelpr` solves three of the most common annoyances.

- Formatting decimals as percentages 
- Calculating percent change between two values
- Clamping values within a specified range

## The Dataset 

We will use the built-in `sales_data` dataset to demonstrate each function. 

```{r}
sales_data
```
## `percent()`

Converting a decimal rating to a readable percentage normally requires multiplying by 100 and pasting a `%` sign. `percent()` does this in one step. 

```{r}
percent(sales_data$rating)
```

You can also control the number of decimal places:

```{r}
percent(sales_data$rating, digits = 2)
```
## `percent_change()`

Calculating percent change between old and new prices normally requires writing out the formula every time. `percent_change()` handles this cleanly. 

```{r}
percent_change(sales_data$price_old, sales_data$price_new)
```

Positive values indicate a price increase, negative values a decrease. 

## `clamp()`

Sometimes raw scores need to be restricted to a valid range. `clamp()` caps values between a lower and upper bound. 

```{r}
clamp(sales_data$raw_score, lower = 0, upper = 2)
```

Any values below 0 is set to 0, and any value above 2 is set to 2. 
